ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-07 paper/paper.tex
update

We only applied stacking on task 2 but not task 1.
We tried two stacking method seperately:
\begin{enumerate}
 \item 2-folds stacking split by two time frames

@@

\textbf{Fig. 1} shows the AUC perfomance of 5-folds Cross Validation and 30\% of testing data using same parameters and seed.
 There is a strong correlation in AUC between Cross Validation and 30\% of testing data.
 AUC is improved once stacking is applied and we included more randomized stacking feature until there is no improvement in AUC.

\begin{figure}[ht!]
\centering
\includegraphics[width=115mm]{Rplot.png}
\caption{AUC of CV result and 30\% testing data using different number of stacking features. One standard deviation of the CV score is plotted via error bar. \label{overflow}}
\end{figure}

@@

\begin{table}[h!]
  \centering
  \caption{Parameters Optimization for XGboost}
  \label{tab:table1}
  \begin{tabular}{p{3cm}p{3cm}p{4cm}p{2cm}}
    \toprule
    Parameters & Description & Range of values & Final Choice \\
    \midrule
    $eta$ & Shrinkage & [0.005, 0.01, 0.05, 0.1] & 0.005 \\
    $max\_depth$ & Maximum depth of trees & [3, 4, 5, 6, 7, 8] & 3 \\
    $colsample\_bytree$ & Subsample ratio of columns when constructing each tree & [0.8, 0.85, 0.9, 0.95, 1] & 0.9 \\
    $colsample\_bylevel$ & Subsample ratio of columns for each split, in each level & [0.8, 0.85, 0.9, 0.95, 1] & 1 \\
    $subsample$ & Subsample ratio of data when constructing each tree & [0.7, 0.8, 0.9, 1] & 1 \\
    $gamma$ & Minimum loss reduction required to make a further partition & [0, 0.025, 0.05, 0.1, 0.3] & 0 \\
    $min\_child\_weight$ & minimum sum of instance weight (Hessian) required to make a further partition & [1, 3, 5, 7] & 1 \\
    $lambda$ & L2 regularization & [0.1, 0.5, 1, 5, 10, 20] & 5 \\
    $alpha$ & L1 regularization & [0, 0.1, 0.5, 1, 5, 10] & 0 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

We only applied stacking on task 2 but not task 1.
We tried two stacking method separately:
\begin{enumerate}
 \item 2-folds stacking split by two time frames

@@

\textbf{Fig. 1} shows the AUC performance of 5-folds Cross Validation and 30\% of testing data using same parameters and seed.
 There is a strong correlation in AUC between Cross Validation and 30\% of testing data.
 AUC is improved once stacking is applied and we included more randomized stacking features until there is no improvement in AUC.

\begin{figure}[ht!]
\centering
\includegraphics[width=110mm]{Rplot.png}
\caption{AUC of CV result and 30\% testing data using different number of stacking features. One standard deviation of the CV score is plotted via error bar. \label{overflow}}
\end{figure}

@@

\begin{table}[h!]
  \centering
  \caption{Parameters Optimization for XGboost}
  \label{tab:table1}
  \begin{tabular}{p{3cm}p{4.5cm}p{4cm}p{1cm}}
    \toprule
    Parameters & Description & Range of values & Final Choice \\
    \midrule
    $eta$ & Shrinkage & [0.005, 0.01, 0.05, 0.1] & 0.005 \\
    $max\_depth$ & Maximum depth of trees & [3, 4, 5, 6, 7, 8] & 3 \\
    $colsample\_bytree$ & Subsample ratio of columns when constructing each tree & [0.8, 0.85, 0.9, 0.95, 1] & 0.9 \\
    $colsample\_bylevel$ & Subsample ratio of columns for each split, in each level & [0.8, 0.85, 0.9, 0.95, 1] & 1 \\
    $subsample$ & Subsample ratio of data when constructing each tree & [0.7, 0.8, 0.9, 1] & 1 \\
    $gamma$ & Minimum loss reduction required to make a further partition & [0, 0.025, 0.05, 0.1, 0.3] & 0 \\
    $min\_child\_weight$ & minimum sum of instance weight (Hessian) required to make a further partition & [1, 3, 5, 7] & 1 \\
    $lambda$ & L2 regularization & [0.1, 0.5, 1, 5, 10, 20] & 5 \\
    $alpha$ & L1 regularization & [0, 0.1, 0.5, 1, 5, 10] & 0 \\
    \bottomrule
  \end{tabular}
\end{table}
